ODGI: scalable tools for pangenome graphs

### 2021-06-02 manuscript/main.tex
Removed extra citations

    Pangenome graphs stand to become a ubiquitous tool in
    genomics~\citep{Eizenga:2020}. With \odgi\ we implemented a
    state-of-the-art tool suite that can transform, analyse and
    visualise pangenome graphs at large scale. \odgi\ also exposes an
    extensible API that can be used by other tools, e.g., for genotyping,
    pangenome graph building \citep{pggb} and normalization \citep {smoothxg}.
    Future work will add support for RNA and protein sequences and
    expand on metadata capabilities of large pangenome graphs.

>>>>

    Pangenome graphs stand to become a ubiquitous tool in
    genomics~\citep{Eizenga:2020}. With \odgi\ we implemented a
    state-of-the-art tool suite that can transform, analyse and
    visualise pangenome graphs at large scale. \odgi\ also exposes an
    extensible API that can be used by other tools, e.g., for
    genotyping, pangenome graph building and normalization.  Future
    work will add support for RNA and protein sequences and expand on
    metadata capabilities of large pangenome graphs.
